### 2018-11-07 Sections/QTCP_protocol_stack.tex
Finished indexing hierarchy

\textsc{Packet Header} is purely classical and needn't be transmitted over the costly quantum network, instead being transmitted over a complementary classical network, running in parallel to, and synchronised with the quantum network. \textsc{Packet Header} contains no information content from \textsc{Data}, instead comprising only metadata relevant to the higher levels of the protocol stack. In particular, \textsc{Packet Header} contains the following fields:
\begin{itemize}
    \item \textsc{Header Size}\index{Header size}: The number of bits in the \textsc{Packet Header}.
    \item \textsc{Message ID}\index{Message ID}: A unique identifier for the complete message to which this \textsc{Packet} belongs. This field mitigates ambiguity as to which \textsc{Message} this packet belongs when performing \textsc{Reconstruction}.
    \item \textsc{Lifetime}\index{Lifetime}: How long the \textsc{Packet} has been in existence for, i.e since it was initially sent by the \textsc{Sender}. This is used by strategies to prevent collisions.
    \item \textsc{Sender}\index{Sender}: A unique node identifier for the sender (Alice).
    \item \textsc{Recipient}\index{Recipient}: A unique node identifier for the recipient (Bob).
    \item \textsc{Order}\index{Order}: To which block taken from \textsc{Data} does this \textsc{Packet Data} belong? This is extremely important in networks where \textsc{Packets} may arrive out of order. The \textsc{Order} field forms the basis for the \textsc{Reconstruction} layer.
    \item \textsc{Quantum Block Size}\index{Quantum block size}: The number of qubits contained in the \textsc{Quantum} component of \textsc{Packet Data}. This is important for the \textsc{Reconstruction} layer.
    \item \textsc{Classical Block Size}\index{Classical block size}: The number of bits contained in the \textsc{Classical} component of \textsc{Packet Data}, also important for the \textsc{Reconstruction} layer.
    \item \textsc{Routing Queue}\index{Routing queues}: A first in, first out (FIFO) queue of node identifiers, tracing out the entire route for the \textsc{Packet} to follow, in chronological order from the next node to visit all the way to the \textsc{Recipient}.
    \item \textsc{Costs}\index{Costs}: A tuple characterising all the accumulated costs of the \textsc{Packet} at the current stage in the route. These are treated as accumulators that are incremented appropriately after each step, since costs are additive.
    \item \textsc{Attributes}\index{Attributes}: A tuple characterising all the non-\textsc{Cost} properties associated with the \textsc{Packet}. Examples include: the \textsc{Priority} of routing a \textsc{Packet} to its destination; suggesting a preferred routing \textsc{Strategy}; or, indicating whether or not a \textsc{Resend Until Success} protocol may be applied to this \textsc{Packet}.
    \item \textsc{Padding}\index{Padding}: Null data to pad the joint \textsc{Classical Packet Data} and \textsc{Packet Header} fields to be of the same length as the \textsc{Quantum Packet Data}. This ensures that the components of the \textsc{Packet} traversing the quantum and classical channels remain in perfect tandem -- bit for qubit. In Sec.~\ref{sec:transport} we show that this facilitates collision detection without the need to measure quantum states.
    \item \textsc{Checksum}\index{Checksums}: A regular checksum of the entire \textsc{Classical} component of the \textsc{Packet}, including both \textsc{Classical Packet Data} and \textsc{Packet Header}. This also forms a part of the collision detection protocol.
\end{itemize}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndrome measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

>>>>

\textsc{Packet Header} is purely classical and needn't be transmitted over the costly quantum network, instead being transmitted over a complementary classical network, running in parallel to, and synchronised with the quantum network. \textsc{Packet Header} contains no information content from \textsc{Data}, instead comprising only metadata relevant to the higher levels of the protocol stack. In particular, \textsc{Packet Header} contains the following fields:
\begin{itemize}
    \item \textsc{Header Size}\index{Header size}: The number of bits in the \textsc{Packet Header}.
    \item \textsc{Message ID}\index{Message ID}: A unique identifier for the complete message to which this \textsc{Packet} belongs. This field mitigates ambiguity as to which \textsc{Message} this packet belongs when performing \textsc{Reconstruction}.
    \item \textsc{Lifetime}\index{Lifetime}: How long the \textsc{Packet} has been in existence for, i.e since it was initially sent by the \textsc{Sender}. This is used by strategies to prevent collisions.
    \item \textsc{Sender}\index{Sender}: A unique node identifier for the sender (Alice).
    \item \textsc{Recipient}\index{Recipient}: A unique node identifier for the recipient (Bob).
    \item \textsc{Order}\index{Order}: To which block taken from \textsc{Data} does this \textsc{Packet Data} belong? This is extremely important in networks where \textsc{Packets} may arrive out of order. The \textsc{Order} field forms the basis for the \textsc{Reconstruction} layer.
    \item \textsc{Quantum Block Size}\index{Quantum block size}: The number of qubits contained in the \textsc{Quantum} component of \textsc{Packet Data}. This is important for the \textsc{Reconstruction} layer.
    \item \textsc{Classical Block Size}\index{Classical block size}: The number of bits contained in the \textsc{Classical} component of \textsc{Packet Data}, also important for the \textsc{Reconstruction} layer.
    \item \textsc{Routing Queue}\index{Routing!Queues}: A first in, first out (FIFO) queue of node identifiers, tracing out the entire route for the \textsc{Packet} to follow, in chronological order from the next node to visit all the way to the \textsc{Recipient}.
    \item \textsc{Costs}\index{Costs}: A tuple characterising all the accumulated costs of the \textsc{Packet} at the current stage in the route. These are treated as accumulators that are incremented appropriately after each step, since costs are additive.
    \item \textsc{Attributes}\index{Attributes}: A tuple characterising all the non-\textsc{Cost} properties associated with the \textsc{Packet}. Examples include: the \textsc{Priority} of routing a \textsc{Packet} to its destination; suggesting a preferred routing \textsc{Strategy}; or, indicating whether or not a \textsc{Resend Until Success} protocol may be applied to this \textsc{Packet}.
    \item \textsc{Padding}\index{Padding}: Null data to pad the joint \textsc{Classical Packet Data} and \textsc{Packet Header} fields to be of the same length as the \textsc{Quantum Packet Data}. This ensures that the components of the \textsc{Packet} traversing the quantum and classical channels remain in perfect tandem -- bit for qubit. In Sec.~\ref{sec:transport} we show that this facilitates collision detection without the need to measure quantum states.
    \item \textsc{Checksum}\index{Checksums}: A regular checksum of the entire \textsc{Classical} component of the \textsc{Packet}, including both \textsc{Classical Packet Data} and \textsc{Packet Header}. This also forms a part of the collision detection protocol.
\end{itemize}

@@

As an alternative to checksums, we could borrow the notion of quantum error correction (QEC)\index{Quantum error correction (QEC)} and fault-tolerance\index{Fault-tolerance} from quantum computing theory \cite{???}. Here we encode a quantum state into a (polynomially) larger Hilbert space. \textit{Syndrome measurements}\index{Syndrome!Measurements} on some of the states in this larger space allow us to both detect and correct universal error models, such as depolarisation or dephasing, provided that error rates are within the fault-tolerance threshold of the code being employed.

### 2018-11-07 Sections/cloud_quantum_computing.tex
Finished indexing hierarchy

The cluster state (Sec.~\ref{sec:CSQC})\index{Cluster states}, topological code (Sec.~\ref{sec:surface_codes})\index{Topological codes} and quantum random walk (Sec.~\ref{sec:QW})\index{Quantum random walks} models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate. Then only classical communication is required to complete a computation and the quantum information is not localised to any particular node.

>>>>

The cluster state (Sec.~\ref{sec:CSQC})\index{Cluster states}, topological code (Sec.~\ref{sec:surface_codes})\index{Topological!Codes} and quantum random walk (Sec.~\ref{sec:QW})\index{Quantum random walks} models for quantum computation may find themselves to be particularly well-suited to distributed implementation, since they naturally reside on graphs, whose nodes needn't be held locally by a single user, but could instead be shared across multiple hosts with the ability for graph nodes to intercommunicate. Then only classical communication is required to complete a computation and the quantum information is not localised to any particular node.

### 2018-11-07 Sections/cryptowars.tex
Finished indexing hierarchy

Digital signatures can be easily implemented using the RSA protocol\index{RSA protocol}, by reversing the roles of the public and private-keys. Now the public-key can only be used for decrypting a message, and the private-key can only be used for encrypting it. As before, it is computationally hard to infer one from the other. The protocol for sending and verifying a digitally signed message is shown in Alg.~\ref{alg:dig_sig}.

@@

Because this protocol is implemented using ordinary RSA\index{RSA protocol}, albeit with reversed roles for the key-pair, it shares the same security strengths and vulnerabilities as RSA public-key cryptography (Sec.~\ref{sec:attacks_on_class}).

>>>>

Digital signatures can be easily implemented using the RSA protocol\index{RSA encryption!Protocol}, by reversing the roles of the public and private-keys. Now the public-key can only be used for decrypting a message, and the private-key can only be used for encrypting it. As before, it is computationally hard to infer one from the other. The protocol for sending and verifying a digitally signed message is shown in Alg.~\ref{alg:dig_sig}.

@@

Because this protocol is implemented using ordinary RSA\index{RSA encryption!Protocol}, albeit with reversed roles for the key-pair, it shares the same security strengths and vulnerabilities as RSA public-key cryptography (Sec.~\ref{sec:attacks_on_class}).

### 2018-11-07 Sections/economics_of_the_quantum_internet.tex
Finished indexing hierarchy

\begin{definition}[Quantum computational leverage] \label{def:quant_econ_lev}\index{Quantum computational leverage formula}\index{Single-qubit quantum computational leverage}
For the $i$th node, and with scaling function $f_{sc}$, the QCL is defined as the ratio between the unified time-shared and individual classical-equivalent algorithmic runtimes,
\begin{align}
\lambda_i &= \frac{\tau_i}{t_i} \nonumber \\
&= \frac{n_i}{n_\mathrm{global}} \cdot \frac{f_{sc}(n_\mathrm{global})}{f_{sc}(n_i)}, \nonumber \\
&= \frac{\chi_\mathrm{sc}(n_\mathrm{global})}{\chi_\mathrm{sc}(n_i)},\nonumber\\
\lambda_i^\mathrm{dB} &= 10\log_{10}(\lambda_i),
\end{align}
where,
\begin{align}
	n_\mathrm{global} = \sum_{j\in \mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network. The logarithmic version of the representation in decibels is simply a convenience when dealing with exponential scaling functions.
\end{definition}

@@

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation\index{Encrypted quantum computation} and be subject to verification protocols\index{Verification protocols}.

@@

We now consider the effect of taxation on quantum resources, specifically in the form of a \textit{qubit tax}\index{Qubit tax} -- a sales tax on the purchase of physical qubits. Although this model of taxation is unlikely to be implemented as we describe, it serves as an insightful test-bed for thought experiments into the qualitative implications of taxing quantum assets.

>>>>

\begin{definition}[Quantum computational leverage] \label{def:quant_econ_lev}\index{Quantum computational leverage!Formula}\index{Single-qubit quantum computational leverage}
For the $i$th node, and with scaling function $f_{sc}$, the QCL is defined as the ratio between the unified time-shared and individual classical-equivalent algorithmic runtimes,
\begin{align}
\lambda_i &= \frac{\tau_i}{t_i} \nonumber \\
&= \frac{n_i}{n_\mathrm{global}} \cdot \frac{f_{sc}(n_\mathrm{global})}{f_{sc}(n_i)}, \nonumber \\
&= \frac{\chi_\mathrm{sc}(n_\mathrm{global})}{\chi_\mathrm{sc}(n_i)},\nonumber\\
\lambda_i^\mathrm{dB} &= 10\log_{10}(\lambda_i),
\end{align}
where,
\begin{align}
	n_\mathrm{global} = \sum_{j\in \mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network. The logarithmic version of the representation in decibels is simply a convenience when dealing with exponential scaling functions.
\end{definition}

@@

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation\index{Encrypted quantum computation} and be subject to verification protocols\index{Verification!Protocols}.

@@

We now consider the effect of taxation on quantum resources, specifically in the form of a \textit{qubit tax}\index{Taxation} -- a sales tax on the purchase of physical qubits. Although this model of taxation is unlikely to be implemented as we describe, it serves as an insightful test-bed for thought experiments into the qualitative implications of taxing quantum assets.

### 2018-11-07 Sections/entanglement_the_ultimate_quantum_resource.tex
Finished indexing hierarchy

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol (UDP)}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

>>>>

What's the advantage of this approach to quantum networking? Why specialise in entanglement distribution, rather than implementing more capable networks with the ability to perform arbitrary operations? There are numerous:
\begin{enumerate}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure.
\item The entanglement servers are entirely passive, not involved interactively with clients.
\item The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user. It acts purely as a provider of a single resource, remaining uninvolved in their subsequent applications.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale. For example, mass production of simple ground-based Bell state relays, or the construction of a comprehensive globe-enveloping constellation of satellites, would inevitably improve economies of scale.
\item Unlike generic quantum states, Bell pairs, GHZ states and cluster states are known states that are infinitely reproducible, without having to worry about no-cloning\index{No-cloning theorem} limitations.
\item Photonic Bell pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Small entangled states like Bell pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology that has already been well-demonstrated on Earth and in space \cite{???}.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP\index{User Datagram Protocol (UDP)}) -- since every state is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We also call this the \textsc{Shotgun}\index{Shotgun!State preparation} approach -- keep firing away until we hit something, and if we lose a few, who cares?
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation (Sec.~\ref{sec:teleport}) mediated by Bell states, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{enumerate}

### 2018-11-07 Sections/essay_NISQ_QC.tex
Indexing up to N
Finished indexing hierarchy

For many problems, there is a big gap between the approximation achieved by classical algorithms and the barrier of exact-case \textbf{NP}-hardness. We do not expect quantum computers to efficiently solve worst-case \textbf{NP}-hard problems, however, quantum devices may be able to find better \textit{approximate} solutions to such problems, or at least find such approximations more quickly. The vision for using NISQ to solve optimisation problems is a hybrid quantum-classical algorithm\index{Hybrid algorithms}. In this scheme we use the quantum device to produce and manipulate an $n$-qubit state, measure the qubits, then process the measurement outcomes classically. This then is utilised as feedback for the next round of quantum state preparation and evolution. The cycle is repeated until convergence is obtained to a quantum state from which the approximate answer can be extracted. Two such algorithms are known as \textit{quantum approximate optimisation algorithms} \cite{bib:farhi2014quantum}\index{Quantum approximate optimisation algorithms}, and \textit{variational quantum eigensolvers} \cite{bib:mcclean2016theory}\index{Variational quantum eigensolvers}.

@@

A quantum algorithm has been shown to find an approximate solution to this problem with an exponential speedup \cite{bib:brandao2017quantum, bib:brandao2017exponential}. In this algorithm, the initial state is a thermal state\index{Thermal states} that is a function of the input matrices for the semidefinite program. The success of the implementation depends on whether the particular thermal state can be efficiently prepared. The output is a quantum state, which approximates the optimal matrix. The quantum state can be measured to extract (via sampling) features of this matrix.

>>>>

For many problems, there is a big gap between the approximation achieved by classical algorithms and the barrier of exact-case \textbf{NP}-hardness. We do not expect quantum computers to efficiently solve worst-case \textbf{NP}-hard problems, however, quantum devices may be able to find better \textit{approximate} solutions to such problems, or at least find such approximations more quickly. The vision for using NISQ to solve optimisation problems is a hybrid quantum-classical algorithm\index{Hybrid!Algorithms}. In this scheme we use the quantum device to produce and manipulate an $n$-qubit state, measure the qubits, then process the measurement outcomes classically. This then is utilised as feedback for the next round of quantum state preparation and evolution. The cycle is repeated until convergence is obtained to a quantum state from which the approximate answer can be extracted. Two such algorithms are known as \textit{quantum approximate optimisation algorithms} \cite{bib:farhi2014quantum}\index{Quantum approximate optimisation algorithms}, and \textit{variational quantum eigensolvers} \cite{bib:mcclean2016theory}\index{Variational quantum eigensolvers}.

@@

A quantum algorithm has been shown to find an approximate solution to this problem with an exponential speedup \cite{bib:brandao2017quantum, bib:brandao2017exponential}. In this algorithm, the initial state is a thermal state\index{Thermal!States} that is a function of the input matrices for the semidefinite program. The success of the implementation depends on whether the particular thermal state can be efficiently prepared. The output is a quantum state, which approximates the optimal matrix. The quantum state can be measured to extract (via sampling) features of this matrix.

### 2018-11-07 Sections/essay_to_the_future_QKD.tex
Finished indexing hierarchy

In parallel to hardware development, research efforts are being directed towards finding new QKD protocols which can outperform existing ones. Two of these are high-dimensional (HD) QKD\index{High-dimensional quantum key distribution} and the Round-Robin differential phase-shift protocol (RR-DPS)\index{Round-Robin differential phase-shift protocol}.

@@

The source is typically less vulnerable to attacks because Alice can prepare her quantum states in a protected environment, and we expect that she can characterise her source. Therefore, flaws in state preparation can be easily incorporated into the security proof\index{Security proof}.

Loss-tolerant\index{Loss-tolerance} protocols have been proposed \cite{bib:PhysRevA.90.052314}, and further developed by \cite{bib:PhysRevA.92.032305}, where decoy state\index{Decoy states} QKD with tight finite-key security has been employed. A wide range of imperfections with the laser source have been taken into account \cite{bib:mizutani2015finite}, including intensity fluctuations. A security proof\index{Security proof} has shown that perfect phase randomisation is also not necessary \cite{bib:cao2015discrete}.

>>>>

In parallel to hardware development, research efforts are being directed towards finding new QKD protocols which can outperform existing ones. Two of these are high-dimensional (HD) QKD\index{High-dimensional quantum key distribution} and the Round-Robin differential phase-shift protocol (RR-DPS)\index{Round-Robin!Differential phase-shift protocol}.

@@

The source is typically less vulnerable to attacks because Alice can prepare her quantum states in a protected environment, and we expect that she can characterise her source. Therefore, flaws in state preparation can be easily incorporated into the security proof\index{Security proofs}.

Loss-tolerant\index{Loss-tolerance} protocols have been proposed \cite{bib:PhysRevA.90.052314}, and further developed by \cite{bib:PhysRevA.92.032305}, where decoy state\index{Decoy states} QKD with tight finite-key security has been employed. A wide range of imperfections with the laser source have been taken into account \cite{bib:mizutani2015finite}, including intensity fluctuations. A security proof\index{Security proofs} has shown that perfect phase randomisation is also not necessary \cite{bib:cao2015discrete}.

### 2018-11-07 Sections/introduction.tex
Finished indexing hierarchy

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{NP \& NP-complete}\index{Optimisation}\index{Satisfiability problems} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises both Rivest, Shamir \& Adleman (RSA) and elliptic-curve public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Elliptic-curve cryptography}\index{Public-key cryptography}, the most widely used cryptographic protocols on the internet today.
		\item This problem is believed to be \textbf{NP}-intermediate -- an \textbf{NP} problem that lies outside \textbf{P} (and is therefore classically hard), but which is not \textbf{NP}-complete (the `hardest' of the \textbf{NP} problems).
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological data analysis (Sec.~\ref{sec:TDA}):\index{Topological data analysis}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis\index{Social media network analysis}; consumer behaviour\index{Consumer behaviour}; behavioural dynamics\index{Behavioural dynamics}; neuroscience\index{Neuroscience}; and higher-dimensional signal and image processing\index{Signal \& image processing}.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

The first demonstrations of digital computer networks were nothing more than simple two-party, point-to-point (P2P) communication\index{P2P topology}. However, the internet we have today extends far beyond this, allowing essentially arbitrary worldwide networking across completely ad hoc networks comprising many different mediums, with any number of parties, in an entirely plug-and-play\index{Plug-and-play} and decentralised fashion. Similarly, elementary demonstrations of quantum communication\index{Quantum communication} have been performed across a small number of parties, and much work has been done on analysing quantum channel capacities\index{Quantum channel capacity} in this context \cite{??? channel_capacity}. But, as with digital computing, demand for a future \textit{quantum internet} is foreseeable, enabling the arbitrary communication of quantum resources, between any number of parties, over ad hoc networks.

>>>>

\begin{itemize}
	\item Searching unstructured databases (Sec.~\ref{sec:quantum_search}):\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability \& optimisation problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal 3-\textsc{SAT}\index{3-SAT problem} problem, are \textbf{NP}-complete.}\index{NP \& NP-complete}\index{Optimisation}\index{Satisfiability problems} (Sec.~\ref{sec:optimising_the_world}):
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm} (Sec.~\ref{sec:shors_alg}):
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises both Rivest, Shamir \& Adleman (RSA) and elliptic-curve public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Elliptic-curve cryptography}\index{Public-key cryptography}, the most widely used cryptographic protocols on the internet today.
		\item This problem is believed to be \textbf{NP}-intermediate -- an \textbf{NP} problem that lies outside \textbf{P} (and is therefore classically hard), but which is not \textbf{NP}-complete (the `hardest' of the \textbf{NP} problems).
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation} (Sec.~\ref{sec:quantum_sim_alg}):
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological data analysis (Sec.~\ref{sec:TDA}):\index{Topological!Data analysis}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis\index{Social media network analysis}; consumer behaviour\index{Consumer behaviour}; behavioural dynamics\index{Behavioural dynamics}; neuroscience\index{Neuroscience}; and higher-dimensional signal and image processing\index{Signal \& image processing}.
		\end{itemize}
	\item Solving linear systems of equations (Sec.~\ref{sec:linear_systems}):\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning (Sec.~\ref{sec:quantum_mind}):\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity \latinquote{Ne obliviscaris.}
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

The first demonstrations of digital computer networks were nothing more than simple two-party, point-to-point (P2P) communication\index{P2P topology}. However, the internet we have today extends far beyond this, allowing essentially arbitrary worldwide networking across completely ad hoc networks comprising many different mediums, with any number of parties, in an entirely plug-and-play\index{Plug-and-play} and decentralised fashion. Similarly, elementary demonstrations of quantum communication\index{Quantum communication} have been performed across a small number of parties, and much work has been done on analysing quantum channel capacities\index{Quantum channels!Capacity} in this context \cite{??? channel_capacity}. But, as with digital computing, demand for a future \textit{quantum internet} is foreseeable, enabling the arbitrary communication of quantum resources, between any number of parties, over ad hoc networks.
